% \begin{tabular}{m{2.4cm} |m{0.3cm} m{15cm}} 
% % \\\multicolumn{2}{c}{} \\
%  \emph{Contributed} & &

 \begin{etaremune}[leftmargin=40pt,labelsep=10pt]
 
%  Photometric Redshifts from SDSS Images with an Interpretable Deep Capsule Network, DESC Photo-z telecon, February 2022
% Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression, DESC Photo-z telecon March 2022
% Calibrated Probability Distributions for Photometric Redshifts, DESC Photo-z telecon July 2022
%%%%% TO ADD:
\item \textit{Uncertainty Quantification for the Physical Sciences}. Brown Bag Seminar, Dept. of Statistical Sciences, University of Toronto, Canada, September 2024.
     \item \textit{Calibrated predictive distributions for photometric redshifts}, Talk at STATSTRO 2024: The AIstronomy Revolution, Toronto, Canada, May 2024.
    \item \textit{Calibrated predictive distributions for photometric redshifts}, Talk at the Summer 2024 LSST-ISSC Collaboration Meeting, Boston, USA, April 2024.
    \item \textit{Photometric Redshifts for Next Generation of Sky Surveys}, Thesis Talk at the 243rd Meeting of the American Astronomical Society, New Orleans, USA, January 2023.
    \item \textit{DESI for photo-$z$ Training and Calibration}, Talk at the 2023 Summer DESC Collaboration Meeting. SLAC National Accelerator Laboratory, USA, July 2023.
    \item \textit{Calibrated predictive distributions for photometric redshifts}, Talk at Statistical Challenges in Modern Astronomy (SCMA) VIII, Pennsylvania State University, State College, USA, June 2023.
    \item \textit{DESI Deep Spectroscopy for Photo-z Training and Calibration}. Talk at DESI-2/ Stage-5 Workshop, Napa, USA, March 2023.
    \item \textit{Stellar Masses using Random Forests}. Talk at DESI Collaboration Meeting, Cancun, Mexico, December 2022.
    \item \textit{Calibration of Individual Photometric Redshift Estimates}. Talk at Essential Cosmology for the Next Generation VIII (Cosmology on the Beach), Playa De Carmen, Mexico, November 2022.
    \item \textit{The Dark Energy Spectroscopic Instrument: One year and 13 million redshifts later}. Astrosnacks presentation, University of Pittsburgh, September 2022.
    \item \textit{Calibrated Probability Distributions for Photometric Redshifts}. Poster at Rubin Observatory Project and Community Workshop, Tucson, USA, August 2022.
    \item \textit{Calibrated Probability Distributions for Photometric Redshifts}. Poster and Talk at Summer 2022 LSST-DESC Collaboration meeting at Kavli Institute for Cosmological Physics, University of Chicago, Chicago, USA, August 2022.
    \item \textit{Calibrated Predictive Distributions for Photometric Redshifts}. Poster at ICML 2022 Workshop on Machine Learning for Astrophysics, Baltimore, USA, July, 2022.
    \item \textit{Recalibrating Probability Density Estimates Using Feature-Space Regression}. Refereed talk at the Symposium on Data Science and Statistics, Pittsburgh, USA, June 2022.
    \item \textit{Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression}. Poster and Talk at the Fourth Workshop on Machine Learning and the Physical Sciences (NeurIPS 2021), December 2021.
    \item \textit{Interpretable Photometric Redshifts using Deep Capsule Networks}. Talk at the 2nd Symposium on Artificial Intelligence for Science, Industry, and Society (AISIS 2021), October 2021.
     \item \textit{Latent Variable Models: Principal Components}. Talk at AstroPGH-TAMU Bootcamp 2021.
    \item \textit{Interpretable Photometric Redshifts with a DeepCapsule Network}. Poster at Statistical Challenges in Modern Astronomy VII, June 2021.
    \item \textit{Mapping the Universe using Sky Surveys}. Astrosnacks presentation, University of Pittsburgh, July 2020.
    \item \textit{Ancillary Targets: Testing filler samples in Survey validation}. DESI Collaboration meeting, Ohio State University, December 2019.
    \item \textit{LRG \& ELG Imaging systematic Trends} (with A. Raichoor). DESI virtual collaboration meeting, March 2020.
\end{etaremune}
% \\\multicolumn{2}{c}{} \\

% \end{tabular}