% \hspace{-0.5in}
% \begin{tabular}{m{2.4cm} m{0.3cm}|m{0.3cm} m{13.8cm}}
%  \emph{Lead/Significant Contributing Author} & & &
 % \mysubsection{Lead/Significant Contributing Author}
 \begin{enumerate}
    \item S. Bhattacharjee, \textbf{B. Dey} and A.K. Mohapatra, 2018, Eur. J. Phys., 39, 035404.\\ \textrm{\textit{Study of geometric phase using classical coupled oscillators}}. \href{https://arxiv.org/abs/2110.15711}{arXiv:2110.15711}.
    \\ Contribution: Developed components of the experimental apparatus, conducted the experiments, and helped with the writing of the article.
    
     \item \textbf{B. Dey}, E. Rosolowsky, Y. Cao, et al., 2019, MNRAS, 488, 2.\\ \textrm{\textit{The EDGE-CALIFA survey: exploring the star formation law through variable selection}}. \href{https://arxiv.org/abs/1906.02273}{arXiv:1906.02273}.
     \\ Contribution: Led the data analysis, interpreted the results, and wrote the paper. 
     
      \item \textbf{B. Dey}, J. A. Newman, B. H. Andrews, et al., 2021, Fourth Workshop on Machine Learning and the Physical Sciences (NeurIPS 2021).\\ \textrm{\textit{Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression}}. \href{https://arxiv.org/abs/2110.15209}{arXiv:2110.15209}.
         \\ Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.

         
       \item T. Chen, \textbf{B. Dey}, A. Ghosh, et al., Proceedings of the US Community Study on the Future of Particle Physics (Snowmass 2021).\\ \textrm{\textit{Interpretable Uncertainty Quantification in AI for HEP.}} \href{https://arxiv.org/abs/2208.03284}{arXiv:2208.03284}.
         \\ Contribution: Drafted the sections pertaining to astrophysics and cosmology and managed the effort to ensure timely submission. 

         
        \item \textbf{B. Dey}, J. A. Newman, B. H. Andrews, et al., 2022, MNRAS, 515, 4.\\ \textrm{\textit{Photometric redshifts from SDSS images with an interpretable deep capsule network}}. \href{https://arxiv.org/abs/2112.03939}{arXiv:2112.03939}.
         \\ Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.
         
         
        \item R. Zhou, \textbf{B. Dey}, J. A. Newman, et al., 2023, AJ, 165, 58.\\ \textrm{\textit{Target Selection and Validation of DESI Luminous Red Galaxies}}. \href{https://arxiv.org/abs/2208.08515}{arXiv:2208.08515}.
         \\ Contribution: Worked on optimizing the design of the data set presented in this paper (i.e., optimized the selection cuts, developed ML based stellar mass estimates which were used to ensure mass completeness of the sample and checked dependence of selection on imaging systematics), analyzed telescope data to validate the sample and contributed to the draft of the paper.

         
        \item D. J. Setton, \textbf{B. Dey}, G. Khullar, et al., 2023, ApJL, 947, L31.\\ \textrm{\textit{DESI Survey Validation Spectra Reveal an Increasing Fraction of Recently Quenched Galaxies at $z\sim 1$}}. \href{https://arxiv.org/abs/2212.05070}{arXiv:2212.05070}.
         \\ Contribution: Helped to collect and process the data sets used, worked on the initial prototype of the project, and helped drafting the paper. 
         

         \item \textbf{B. Dey}, D. Zhao, J. A. Newman, et al. 2022, Submitted to Annals of Applied Statistics.\\
    \textrm{\textit{Conditionally Calibrated Predictive Distributions by Probability-Probability Map: Application to Galaxy Redshift Estimation and Probabilistic Forecasting}}.  \href{https://arxiv.org/abs/2205.14568}{arXiv:2205.14568}.
     \\Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.

     
       \item \textbf{B. Dey}, J. A. Newman, DESI Collaboration et al. 2023, \textit{in prep}, expected submission by Nov. 2023.\\
    \textrm{\textit{DESI Deep Spectroscopy for Photometric Redshift Training and Calibration for LSST}}. % \href{https://arxiv.org/abs/2205.14568}{arXiv:2205.14568}.
 \\ Contribution: Conceptualized the project, worked to secure telescope time to acquire the data, led the data analysis and drafted the paper. 
    
   
\end{enumerate}
 


% 