% \hspace{-0.5in}
% \begin{tabular}{m{2.4cm} m{0.3cm}|m{0.3cm} m{13.8cm}}
%  \emph{Lead/Significant Contributing Author} & & &
 \mysubsection{Lead/Significant Contributing Author}
 \begin{etaremune}[leftmargin=40pt,labelsep=10pt]

    \item \textbf{B. Dey}, J. A. Newman, DESI Collaboration et al. 2023, \textit{in prep}, expected submission by Nov. 2023.\\
    \textrm{\textit{DESI Deep Spectroscopy for Photometric Redshift Training and Calibration for LSST}}. % \href{https://arxiv.org/abs/2205.14568}{arXiv:2205.14568}.
     \\Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.
    
    
    \item \textbf{B. Dey}, D. Zhao, J. A. Newman, et al. 2022, Submitted to Annals of Applied Statistics.\\
    \textrm{\textit{Conditionally Calibrated Predictive Distributions by Probability-Probability Map: Application to Galaxy Redshift Estimation and Probabilistic Forecasting}}.  \href{https://arxiv.org/abs/2205.14568}{arXiv:2205.14568}.
     \\Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.
    
    \item D. J. Setton, \textbf{B. Dey}, G. Khullar, et al., 2023, ApJL, 947, L31.\\ \textrm{\textit{DESI Survey Validation Spectra Reveal an Increasing Fraction of Recently Quenched Galaxies at $z\sim 1$}}. \href{https://arxiv.org/abs/2212.05070}{arXiv:2212.05070}.
     \\ Contribution: Helped to collect and process the data sets used, worked on the initial prototype of the project, and helped drafting the paper. 
    
    \item R. Zhou, \textbf{B. Dey}, J. A. Newman, et al., 2023, AJ, 165, 58,.\\ \textrm{\textit{Target Selection and Validation of DESI Luminous Red Galaxies}}. \href{https://arxiv.org/abs/2208.08515}{arXiv:2208.08515}.
     \\ Contribution: Worked on optimizing the design of the data set presented in this paper (i.e., optimized the selection cuts, developed ML based stellar mass estimates which were used to ensure mass completeness of the sample and checked dependence of selection on imaging systematics), analyzed telescope data to validate the sample and contributed to the draft of the paper.
    
    \item \textbf{B. Dey}, J. A. Newman, B. H. Andrews, et al., 2022, MNRAS, 515, 4.\\ \textrm{\textit{Photometric redshifts from SDSS images with an interpretable deep capsule network}}. \href{https://arxiv.org/abs/2112.03939}{arXiv:2112.03939}.
     \\ Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.
    
    \item T. Chen, \textbf{B. Dey}, A. Ghosh, et al., Proceedings of the US Community Study on the Future of Particle Physics (Snowmass 2021).\\ \textrm{\textit{Interpretable Uncertainty Quantification in AI for HEP.}} \href{https://arxiv.org/abs/2208.03284}{arXiv:2208.03284}.
     \\ Contribution: Drafted the sections pertaining to astrophysics and cosmology and managed the effort to ensure timely submission. 
    
    \item \textbf{B. Dey}, J. A. Newman, B. H. Andrews, et al., 2021, Fourth Workshop on Machine Learning and the Physical Sciences (NeurIPS 2021).\\ \textrm{\textit{Re-calibrating Photometric Redshift Probability Distributions Using Feature-space Regression}}. \href{https://arxiv.org/abs/2110.15209}{arXiv:2110.15209}.
    \\ Contribution: Led the development of the methodology and associated code, demonstrated the efficacy of the method on real-world examples, and wrote the paper.
    
    \item \textbf{B. Dey}, E. Rosolowsky, Y. Cao, et al., 2019, MNRAS, 488, 2.\\ \textrm{\textit{The EDGE-CALIFA survey: exploring the star formation law through variable selection}}. \href{https://arxiv.org/abs/1906.02273}{arXiv:1906.02273}.
    \\ Contribution: Led the data analysis, interpreted the results, and wrote the paper. 
    
    \item S. Bhattacharjee, \textbf{B. Dey} and A.K. Mohapatra, 2018, Eur. J. Phys., 39, 035404.\\ \textrm{\textit{Study of geometric phase using classical coupled oscillators}}. \href{https://arxiv.org/abs/2110.15711}{arXiv:2110.15711}.
    \\ Contribution: Developed components of the experimental apparatus, conducted the experiments, and helped with the writing of the article.
\end{etaremune}
 

% \end{tabular}
 
%  \begin{tabular}{m{2.4cm} m{0.3cm}|m{0.3cm} m{13.8cm}}
 
%  \emph{Contributing Author} & & &
\clearpage
 \mysubsection{Contributing Author}
 \begin{etaremune}[leftmargin=40pt,labelsep=10pt]
 \item R. Zhou, S. Ferraro, M. White et al.[including \textbf{B. Dey}]. Submitted to JCAP.\\ \textrm{\textit{DESI luminous red galaxy samples for cross-correlations}}. \href{https://arxiv.org/abs/2309.06443}{arXiv:2309.06443}
 
 \item M.J. Yantovski-Barth, J.A. Newman, \textbf{B. Dey}, et al. Submitted to MNRAS.\\ \textrm{\textit{The CluMPR Galaxy Cluster-Finding Algorithm and DESI Legacy Survey Galaxy Cluster Catalogue}}. \href{https://arxiv.org/abs/2307.10426}{arXiv:2307.10426}.
 
 \item J. Han, A. Dey, A. Price-Whelan et al.[including \textbf{B. Dey}]. 2023, Submitted to the call for white papers for the Roman Core Community Survey, and to the Bulletin of the AAS. \\ \textrm{\textit{NANCY: Next-generation All-sky Near-infrared Community surveY}}. \href{https://arxiv.org/abs/2306.06315}{arXiv:2306.06315 }.

 \item DESI Collaboration, et al.[including \textbf{B. Dey}]. Submitted to AJ.\\ \textrm{\textit{Validation of the Scientific Program for the Dark Energy Spectroscopic Instrument}}. \href{https://arxiv.org/abs/2306.06307}{arXiv:2306.06307}.
 
  \item DESI Collaboration, et al.[including \textbf{B. Dey}]. Submitted to AJ.\\ \textrm{\textit{The Early Data Release of the Dark Energy Spectroscopic Instrument}}. \href{https://arxiv.org/abs/2306.06308}{arXiv:2306.06308}.

 \item F. Prada, J. Ereza, A. Smith et al.[including \textbf{B. Dey}]. Submitted to MNRAS.
 \\ \textrm{\textit{The DESI One-Percent Survey: Modelling the clustering and halo occupation of all four DESI tracers with Uchuu}}. \href{https://arxiv.org/abs/2306.06308}{arXiv:2306.06308}.
 
 \item E. Chaussidon, C. Y\`eche, N. Palanque-Delabrouille et al.[including \textbf{B. Dey}], 2023, ApJ, 944, 1. \\ \textrm{\textit{Target Selection and Validation of DESI Quasars}}. \href{https://arxiv.org/abs/2208.08511}{arXiv:2208.08511}.
 
 \item C. Hahn, M. J. Wilson, O. Ruiz-Macias et al.[including \textbf{B. Dey}], 2023, AJ, 165, 6. \\ \textrm{\textit{DESI Bright Galaxy Survey: Final Target Selection, Design, and Validation}}. \href{https://arxiv.org/abs/2208.08512}{arXiv:2208.08512}.
 
 \item A. Raichoor, J. Moustakas, J. A. Newman et al.[including \textbf{B. Dey}], 2023, AJ, 165, 3. \\ \textrm{\textit{Target Selection and Validation of DESI Emission Line Galaxies}}. \href{https://arxiv.org/abs/2208.08513}{arXiv:2208.08513}.
 
 \item T. Lan, R. Tojeiro, E. Armengaud et al.[including \textbf{B. Dey}], 2023, ApJ, 943, 1. \\ \textrm{\textit{The DESI Survey Validation: Results from Visual Inspection of Bright Galaxies, Luminous Red Galaxies, and Emission Line Galaxies}}. \href{https://arxiv.org/abs/2208.08516}{arXiv:2208.08516}.
 
 \item D. M. Alexander, T. M. Davis, et al.[including \textbf{B. Dey}], 2023, AJ, 165, 3. \\ \textrm{\textit{The DESI Survey Validation: Results from Visual Inspection of the Quasar Survey Spectra}}. \href{https://arxiv.org/abs/2208.08517}{arXiv:2208.08517}.
 
 \item J. Guy, S. Bailey, A. Kremin, et al.[including \textbf{B. Dey}], 2023, AJ, 165, 4. \\ \textrm{\textit{The Spectroscopic Data Processing Pipeline for the Dark Energy Spectroscopic Instrument}}. \href{https://arxiv.org/abs/2209.14482}{arXiv:2209.14482}.
 
 \item A. D. Myers, J. Moustakas, S. Bailey, et al.[including \textbf{B. Dey}], 2023, AJ, 165, 2. \\ \textrm{\textit{The Target-selection Pipeline for the Dark Energy Spectroscopic Instrument}}. \href{https://arxiv.org/abs/2208.08518}{arXiv:2208.08518}.
 
 \item DESI Collaboration, et al.[including \textbf{B. Dey}], 2022, AJ, 164, 5. \\ \textrm{\textit{Overview of the Instrumentation for the Dark Energy Spectroscopic Instrument}}. \href{https://arxiv.org/abs/2205.10939}{arXiv:2205.10939}.
 
\item K. R. Sand, et al.[including \textbf{B. Dey}], 2022, ApJ, 932, 2. \\ \textrm{\textit{Multiband Detection of Repeating FRB 20180916B}}. \href{https://arxiv.org/abs/2111.02382}{arXiv:2111.02382 }.

\item S Dutta, N Khandai and \textbf{B. Dey}, 2020, MNRAS, 494, 2. \\ \textrm{\textit{The population of galaxies that contribute to the HI mass function}}. \href{https://arxiv.org/abs/1909.03077}{arXiv:1909.03077}.

\item R. Zhou, et al. [including \textbf{B. Dey}], 2020, RNAAS, 4, 10. \\ \textrm{\textit{Preliminary Target Selection for the DESI Luminous Red Galaxy (LRG) Sample}}. \href{https://arxiv.org/abs/2010.11282}{arXiv:2010.11282}.

\item K. R. Sand, et al.[including \textbf{B. Dey}], 2020, ATel, 13781. \\ \textrm{\textit{Low-frequency detection of FRB180916 with the uGMRT}}. \href{https://www.astronomerstelegram.org/?read=13781}{ATel:13781}.
\end{etaremune} 
